Articulation Analysis: The Sound of Teaching Music 1

### 2020-09-25 script/RNotebook/articulation.Rmd
update analysis scripts
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r extract, include = FALSE}
df_ioi <- read.csv("./trimmed/data_ioi.csv", header = T, sep = ",", dec = ".") # read a trimmed csv
df_kot <- read.csv("./trimmed/data_kot.csv", header = T, sep = ",", dec = ".") # read a trimmed csv

@@

@@

# KOT-Order-Articulation
- Investigate whether there is any order effect of the conditions.

## 1. All{#kot_art_order_group_all}
```{r kot_art_order_all, echo = FALSE}
# For each participant
kot_art_order <- aggregate(KOT~SubNr*Condition*Skill*Subcomponent*Order, data = subset(df_kot_art, df_kot_art$Interval != 8 & df_kot_art$Interval != 16 & df_kot_art$Interval != 24 & df_kot_art$Interval != 41 & df_kot_art$Interval != 49 & df_kot_art$Interval != 57), FUN = function(x){round(c(N = length(x), mean = mean(x), sd = sd(x)), 4)})
kot_art_order <- cbind(kot_art_order[,1:5], as.data.frame(kot_art_order[,6]))
# Change colnames
colnames(kot_art_order) <- c("SubNr", "Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD")

# Group mean
kot_art_order_all <- aggregate(Mean~Condition*Skill*Subcomponent*Order, data = kot_art_order,
                                     FUN = function(x){round(c(N = length(x), mean = mean(x), sd = sd(x), sem = sd(x)/sqrt(length(x))), 4)})
kot_art_order_all <- cbind(kot_art_order_all[,1:4], as.data.frame(kot_art_order_all[,5]))
# Change colnames
colnames(kot_art_order_all) <- c("Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD", "SEM")
print(kot_art_order_all)
```

```{r kot_art_order_all_bar, echo = FALSE}
p_kot_art_order_all <- ggplot(data = kot_art_order_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SEM, ymax = Mean + SEM),
                width = .2, position = position_dodge(.9)) +
  facet_wrap(Order ~ .) +
  labs(y = "KOT (ms)", subtitle = "KOT: Articulation")
p_kot_art_order_all
```

#### Box plot
```{r kot_art_order_all_box, echo = FALSE}
p_kot_art_order_all_box <- ggplot(data = kot_art_order, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_boxplot() +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 1, position = position_dodge(.75)) +
  facet_wrap(Order ~ .) +
  labs(y = "KOT", subtitle = "KOT: Articulation")
p_kot_art_order_all_box
```

### Statistics
#### Normality check
```{r normality5, echo = FALSE}
# Normality check
kot_art_order$Subcomponent <- factor(kot_art_order$Subcomponent)
kot_art_order_norm <- by(kot_art_order$Mean, list(kot_art_order$Condition, kot_art_order$Subcomponent, kot_art_order$Order), shapiro.test)
print(kot_art_order_norm)
```

#### Three-way ANOVA (ez)
```{r stats9, echo = FALSE}
kot_art_order_aov <- ezANOVA(
  data = df_kot_art
  , dv = .(KOT)
  , wid = .(SubNr)
  , between = .(Order)
  , within = .(Condition, Subcomponent)
  , type = 3
  , detailed = TRUE
)
kot_art_order_aov$ANOVA$F <- round(kot_art_order_aov$ANOVA$F, 4)
kot_art_order_aov$ANOVA$p <- round(kot_art_order_aov$ANOVA$p, 4)
print(kot_art_order_aov)
```

>>>>

```{r file, include = FALSE}
filename_ioi = "../R/preprocessor/trimmed/data_ioi_1.txt"
filename_kot = "../R/preprocessor/trimmed/data_kot.txt"
```

```{r extract, include = FALSE}
df_ioi <- read.csv(filename_ioi, header = T, sep = ",", dec = ".") # read a trimmed csv
df_kot <- read.csv(filename_kot, header = T, sep = ",", dec = ".") # read a trimmed csv

@@

# exclude participants
df_ioi <- df_ioi %>% dplyr::filter(SubNr != 1 & SubNr != 3 & SubNr != 14 & SubNr != 16)
df_kot <- df_kot %>% dplyr::filter(SubNr != 1 & SubNr != 3 & SubNr != 14 & SubNr != 16)

@@

<!-- # KOT-Order-Articulation -->
<!-- - Investigate whether there is any order effect of the conditions. -->

<!-- ## 1. All{#kot_art_order_group_all} -->
<!-- ```{r kot_art_order_all, echo = FALSE} -->
<!-- # For each participant -->
<!-- kot_art_order <- aggregate(KOT~SubNr*Condition*Skill*Subcomponent*Order, data = subset(df_kot_art, df_kot_art$Interval != 8 & df_kot_art$Interval != 16 & df_kot_art$Interval != 24 & df_kot_art$Interval != 41 & df_kot_art$Interval != 49 & df_kot_art$Interval != 57), FUN = function(x){round(c(N = length(x), mean = mean(x), sd = sd(x)), 4)}) -->
<!-- kot_art_order <- cbind(kot_art_order[,1:5], as.data.frame(kot_art_order[,6])) -->
<!-- # Change colnames -->
<!-- colnames(kot_art_order) <- c("SubNr", "Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD") -->

<!-- # Group mean -->
<!-- kot_art_order_all <- aggregate(Mean~Condition*Skill*Subcomponent*Order, data = kot_art_order, -->
<!--                                      FUN = function(x){round(c(N = length(x), mean = mean(x), sd = sd(x), sem = sd(x)/sqrt(length(x))), 4)}) -->
<!-- kot_art_order_all <- cbind(kot_art_order_all[,1:4], as.data.frame(kot_art_order_all[,5])) -->
<!-- # Change colnames -->
<!-- colnames(kot_art_order_all) <- c("Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD", "SEM") -->
<!-- print(kot_art_order_all) -->
<!-- ``` -->

<!-- ### Plot -->
<!-- #### Bar graph -->
<!-- - Error bars show SEM of the mean -->

<!-- ```{r kot_art_order_all_bar, echo = FALSE} -->
<!-- p_kot_art_order_all <- ggplot(data = kot_art_order_all, aes(x = Subcomponent, y = Mean, fill = Condition)) + -->
<!--   geom_bar(stat = "identity", position = position_dodge()) + -->
<!--   geom_errorbar(aes(ymin = Mean - SEM, ymax = Mean + SEM), -->
<!--                 width = .2, position = position_dodge(.9)) + -->
<!--   facet_wrap(Order ~ .) + -->
<!--   labs(y = "KOT (ms)", subtitle = "KOT: Articulation") -->
<!-- p_kot_art_order_all -->
<!-- ``` -->

<!-- #### Box plot -->
<!-- ```{r kot_art_order_all_box, echo = FALSE} -->
<!-- p_kot_art_order_all_box <- ggplot(data = kot_art_order, aes(x = Subcomponent, y = Mean, fill = Condition)) + -->
<!--   geom_boxplot() + -->
<!--   geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 1, position = position_dodge(.75)) + -->
<!--   facet_wrap(Order ~ .) + -->
<!--   labs(y = "KOT", subtitle = "KOT: Articulation") -->
<!-- p_kot_art_order_all_box -->
<!-- ``` -->

<!-- ### Statistics -->
<!-- #### Normality check -->
<!-- ```{r normality5, echo = FALSE} -->
<!-- # Normality check -->
<!-- kot_art_order$Subcomponent <- factor(kot_art_order$Subcomponent) -->
<!-- kot_art_order_norm <- by(kot_art_order$Mean, list(kot_art_order$Condition, kot_art_order$Subcomponent, kot_art_order$Order), shapiro.test) -->
<!-- print(kot_art_order_norm) -->
<!-- ``` -->

<!-- #### Three-way ANOVA (ez) -->
<!-- ```{r stats9, echo = FALSE} -->
<!-- kot_art_order_aov <- ezANOVA( -->
<!--   data = df_kot_art -->
<!--   , dv = .(KOT) -->
<!--   , wid = .(SubNr) -->
<!--   , between = .(Order) -->
<!--   , within = .(Condition, Subcomponent) -->
<!--   , type = 3 -->
<!--   , detailed = TRUE -->
<!-- ) -->
<!-- kot_art_order_aov$ANOVA$F <- round(kot_art_order_aov$ANOVA$F, 4) -->
<!-- kot_art_order_aov$ANOVA$p <- round(kot_art_order_aov$ANOVA$p, 4) -->
<!-- print(kot_art_order_aov) -->
<!-- ``` -->
